---
title: "Causal Map Functions Vignette"
author: "Steve Powell"
output:
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: true
    toc_depth: 3
    number_sections: false
    theme: lumen
---


```{r setup, include=FALSE}
# devtools::load_all();devtools::document();pkgdown::build_site(lazy=F)

options(dplyr.summarise.inform = FALSE)
library(CausalMapFunctions)
library(knitr)
library(htmltools)
library(kableExtra)
library(scales)
knitr::opts_chunk$set(echo = F)
#source("../R/functions.R")################################

pp=function(x,N=99){
  print(x,n=N)
}

replace_null <- function(x,replacement=0){
  if(is.null(x)) replacement else x
}


print_inner_filter <- function(xx){
  # browser()
xx$graf <- NULL
fil <- xx[[1]] %>% unlist %>% str_remove_all("^pipe_") %>% str_replace("_"," ")
xx <- xx[-1]
nams=names(xx)
tibble(names=nams,vals=unlist(xx)) %>% 
  unite(filter,sep="=") %>% 
  pull(filter) %>% 
  unlist %>% 
  paste0(.,collapse=" ") %>% 
  paste0(fil," ",.)
}
print_filter <- function(graf){
  # browser()
  if(is.null(attr(graf,"meta")))return()
story <- attr(graf,"meta")[[1]] %>% keep(~str_detect(.,"^load_mapfile")) %>% unlist %>% str_remove("load_mapfile *path=")
input_ace <- attr(graf,"meta") %>% list_modify("load_mapfile" = NULL) %>% unlist %>% keep(.!=".") %>% map(~str_remove_all(.,"^pipe_") %>% str_replace("_"," ")) %>%  paste0(collapse = "\n")
filters <- paste0("&filters=",URLencode(input_ace %>% replace_null(""),reserved=T))
# browser()
attr(graf,"meta") %>% 
  map(~print_inner_filter(.) %>% 
      str_trim %>% 
      div(style=";")
  ) %>% div(style="padding:10px;background-color:aliceblue;")
  # ) %>% div(a("Link",href=paste0("https://causalmap.shinyapps.io/CausalMap2?story=",story,filters)),style="padding:10px;background-color:aliceblue;")
}

make_interactive_map <- function(graf){
  tagList(print_filter(graf),CausalMapFunctions::make_interactive_map(graf))
}
make_print_map <- function(graf){
  tagList(print_filter(graf),CausalMapFunctions::make_print_map(graf))
}

```

You might need to wait a few seconds for all of the graphics in this file to load.

## How it works

You import a mapfile from a built-in example file, a local excel file, from a S3 store, or from sql using `load_mapfile()`

A family of functions `pipe_*` are provided (manipulate, calculate, hide, combine...) to implement successive filtering operations on a mapfile. These operations do not change the underlying data. 

So you import/load data as a mapfile and all your work steps are then just applying successive filters.

Each filter returns another mapfile, suitably filtered. 

Mapfiles, which are just lists of tables (actually, `tibbles`) with the class `mapfile`. 

Statement tables are used in Causal Map as the underlying data which is to be coded into causal links. So each link refers to a quote from a particular statement. Statements are optional and this package can be used without them.

In this package, nodes are called `factors` and the edges are called `links`.


## Parser

All of these filters can be produced and edited either in a chain of actual R functions or in the simplified text format which is processed by the parser: `parse_commands`.

This parser takes text strings with a simpler command syntax as input and outputs one of these main functions for each line of text. This parser is used to read text commands from the input window in Causal Map Viewer and manipulate the output map with the corresponding functions. The input text can also consist of several lines, and the commands are applied one by one in sequence, in a pipeline of commands, such that after each command, such as each command starts with the map defined by the previous line and produces a new one. 

## Output functions

There are three output functions which are thin wrappers around visNetwork, DiagrammeR and DT, allowing a graph to be displayed using any of these three visualisation engines. 


### Additional fields

Some of the commands such as path tracing create additional fields or variables for each factor and/or link. For example, when filtering by label, fields are created which can then be used to apply formatting. 

## Loading example datasets

(After loading CausalMapFunctions library)


The package ships with some example datasets, at the moment just these:

- example2
- quip_example

which you can also view in Causal Map on the web.


Visualise the files like this:

```{r echo=T}
example2 %>% pipe_coerce_mapfile() %>% make_interactive_map

```



Your input mapfile should have the standard Causal Map [format](guide.causalmap.app/core-tables.html): you can see an example by downloading any of the files in Causal Map on the web.


`pipe_coerce_mapfile` will also process a file with no factors and from_label and to_label columns as a named edgelist.


```{r }
# ll <- quip_example
  # ee <- example2
  ee <- load_mapfile("example2")
```

## Basic examples


### Interactive and Print maps

```{r }  
  ee %>%
    pipe_label_links("link_id",fun = "unique") %>%
    make_interactive_map
  
  ee %>%
    pipe_label_links("link_id",fun = "unique") %>%
    make_print_map()
  ee %>%
    pipe_set_print(grv_layout="circo") %>%
    make_print_map()
```


```{r }
hz <- load_mapfile("health-zoom")%>% pipe_coerce_mapfile 
  so <- load_mapfile("stress-opposites")%>% pipe_coerce_mapfile 
  tt <- load_mapfile("cm1/tearfund-sl")%>% pipe_coerce_mapfile
  ll <- load_mapfile("quip-coded")%>% pipe_coerce_mapfile
  oo <- load_mapfile("organisation1coded")%>% pipe_coerce_mapfile
  e3 <- load_mapfile("example3-path-tracing")%>% pipe_coerce_mapfile
  mm <- load_mapfile("save-the-children-mozambique-copy")%>% pipe_coerce_mapfile
  hh <- load_mapfile("hannahcombiningopposites-sp-test")%>% pipe_coerce_mapfile
```


### Selecting and finding 


If you filter the factors of a mapfile, e.g. show only factors with labels beginning xyz,

- also the links are filtered (removing links to removed factors)
- the statements are not touched

If you filter the links of a mapfile, e.g. show only links with hashtags containing xyz,

- the factors are not filtered (but using a different command you can remove any factors which no longer have any links)
- the statements are not touched

If you filter the statements of a mapfile, e.g. show only statements with texts containing xyz,

- also the links are filtered (removing links to removed statements)
- the factors are filtered




```{r }  
ll %>%
    pipe_select_factors(15) %>%
    make_interactive_map

ll %>%
    pipe_select_factors(15) %>%
    make_interactive_map

```


Simple frequency

```{r }  
ll %>%
    pipe_find_links("simple_frequency",value = 50,"greater") %>%
    make_interactive_map

```


```{r }  
ll %>%
    pipe_select_links(5) %>%
    make_interactive_map

```

```{r }  
ll %>%
    pipe_find_statements(field="statement_id",value=5,operator="equals") %>%
    make_interactive_map
```

```{r }  
ll %>%
    pipe_find_factors(value="economic") %>%
    make_interactive_map
```


#### Zero up and down

```{r }  
ee %>%
    pipe_find_factors(value="rainfall",up=0,down=0,remove_isolated = T) %>%
    make_interactive_map
ee %>%
    pipe_find_factors(value="rainfall",up=0,down=0,remove_isolated = F) %>%
    make_interactive_map

```

#### Case insensitive

```{r }  
ee %>%
    pipe_find_factors(value="business|property") %>%
    make_interactive_map

```

#### Should these work?

```{r }  
ee %>%
    pipe_find_factors(value="business|property") %>%
    make_interactive_map

```

```{r }  
ee %>%
    pipe_find_factors(value="business OR property") %>%
    make_interactive_map

```

### notcontains

```{r }  
ee %>%
    pipe_find_factors(value="sea",operator="notcontains") %>%
    make_interactive_map

```

```{r }  
ee %>%
    pipe_find_factors(value="sea OR High",operator="notcontains") %>%
    make_interactive_map

```
```{r }  
ee %>% pipe_find_statements(value="1",operator="notcontains",field="statement_id")%>%
    make_interactive_map

```

```{r }  
ee %>% pipe_find_statements(value="1",operator="notcontains",field="statement_id")%>%
    make_interactive_map

```

### notequals

```{r }  
ee %>% pipe_find_statements(value="1",operator="notequals",field="statement_id")%>%
    make_interactive_map

```


```{r }  
ee %>%
    pipe_find_factors(value="Coastal erosion",operator="notequals") %>%
    make_interactive_map

```




Does work:

```{r }  
ee %>%
    pipe_find_factors(value="business OR property") %>%
    make_interactive_map

```


Order matters

```{r }  
ll %>%
    pipe_find_factors(value="economic") %>%
    pipe_select_factors(5) %>%
    make_interactive_map

```

No result

```{r }  
ll %>%
    pipe_find_factors(value="asdfasdfasdf") %>%
    make_interactive_map
```



```{r }  
ll %>%
    pipe_find_links(field="from_label",value="economic",operator="contains") %>%
    make_interactive_map
```

### Numerical comparison

```{r }  
ll %>%
    pipe_find_statements(field="statement_id",value=20,operator="less") %>%
    make_interactive_map
```

No result

```{r }  
ll %>%
    pipe_find_statements(field="statement_id",value=20000000,operator="greater") %>%
    make_interactive_map
```

### Highlight only

```{r }  
e3  %>% 
  pipe_find_factors(value="Damage",highlight_only=T) %>% pipe_color_factors(field="found") %>% 
  make_interactive_map()

```

Note this doe sn'twork in the app:

```{r }  
e3  %>% 
  pipe_find_links(field="from_label",value="Damage",highlight_only=T) %>%     
  pipe_color_links(field="found",fun="literal") %>% 
  make_interactive_map()

```
## Conditional formatting

```{r }  
ll %>%
    pipe_select_factors(5) %>%
    pipe_scale_factors(field="frequency") %>%
    make_interactive_map

ll %>%
    pipe_select_factors(5) %>%
    pipe_scale_factors(field="frequency") %>%
    make_print_map
```

```{r }
ll %>%
    pipe_select_factors(5) %>%
    pipe_color_factors(field="frequency") %>%
    pipe_color_borders(field="betweenness") %>%
    pipe_wrap_factors(5) %>%
    make_interactive_map

```

```{r }
ll %>%
    pipe_select_factors(5) %>%
    pipe_color_links(value="count: link_id") %>%
    pipe_wrap_factors(5) %>%
    make_interactive_map

```

```{r }  

ee %>%
    pipe_label_links("from_label",fun = "unique") %>%
    pipe_wrap_links(6) %>%
    make_interactive_map

```

```{r }  

ee %>%
    pipe_label_links(value="unique: from_label") %>%
    pipe_wrap_links(6) %>%
    make_interactive_map

```

```{r }  

ll %>%
    make_interactive_map

```

## Remove brackets

```{r }  
ll %>%
    pipe_select_factors(5) %>%
    pipe_remove_brackets() %>%
    make_interactive_map

```

## Bundle factors

```{r }  
ll %>%
    pipe_bundle_factors(value = "IEA") %>%
    pipe_select_factors(5) %>%
    make_interactive_map



```

## Format links without bundling

```{r }  
ee %>%
  pipe_color_links("link_id",fun = "mean") %>%
  make_interactive_map
ee %>%
  pipe_scale_links("link_id",fun = "mean") %>%
  make_interactive_map

```


## Label links

```{r }  
e3 %>%
  pipe_label_links("link_id",fun = "literal",add_field_name = T) %>%
  make_interactive_map

e3 %>%
  pipe_label_links("link_id",fun = "literal") %>%
  pipe_label_links("from_label",fun = "literal",add_field_name = T,clear_previous = F) %>%
  make_interactive_map

e3 %>%
  pipe_bundle_links() %>% 
  pipe_label_links("link_id",fun = "literal",add_field_name = T) %>%
  make_interactive_map

e3 %>%
  pipe_bundle_links() %>% 
  pipe_label_links("link_id",fun = "literal") %>%
  pipe_label_links("from_label",fun = "literal",clear_previous = F) %>%
  make_interactive_map

e3 %>%
  pipe_bundle_links() %>% 
  parse_commands("label links field=statement_id fun=unique clear_previous=F") %>%
  make_interactive_map


```


## Bundling links

Note the defaults for `bundle_links` and `label_links`:

```{r }  
ll %>%
    pipe_find_factors(value="economic") %>%
    pipe_select_factors(5) %>%
    pipe_bundle_links() %>%
    pipe_label_links() %>%
    make_interactive_map


```

```{r }  
ll %>%
    pipe_find_factors(value="economic") %>%
    pipe_select_factors(5) %>%
    pipe_bundle_links() %>%
    pipe_label_links() %>%
    make_interactive_map


```

Note the default for `bundle_links` is equivalent to simple_bundle:

```{r }  
ll %>%
    pipe_find_factors(value="economic") %>%
    pipe_select_factors(5) %>%
    pipe_bundle_links(group="simple_bundle") %>%
    pipe_label_links() %>%
    make_interactive_map


```

### Group and label by sex and scale by count:

```{r }  
ll %>%
    pipe_select_factors(5) %>%
    pipe_bundle_links(field="1. Sex") %>%
    pipe_scale_links("link_id",fun = "count") %>%
    pipe_label_links("1. Sex",fun = "unique") %>%
    pipe_color_links("1. Sex",fun = "unique") %>%
    make_interactive_map
```

```{r }  
ll %>%
    pipe_select_links(16) %>%
    pipe_bundle_links(field="1. Sex") %>%
    pipe_label_links("link_id",fun = "count") %>%
    make_interactive_map
```


### Group by sex and scale and colour by count:

```{r }  
ll %>%
    pipe_select_factors(5) %>%
    pipe_bundle_links(field="1. Sex") %>%
    pipe_color_links("link_id",fun = "count") %>%
    pipe_scale_links("link_id",fun = "count") %>%
    pipe_label_links("link_id",fun = "count") %>%
    make_interactive_map
```

### Proportion

```{r}
ll %>%    
  pipe_find_factors(value="sed yield") %>%
  pipe_bundle_links(field="District") %>% 
  pipe_color_links(field="District",fun="unique") %>% 
  pipe_label_links(value="percent: link_id") %>%  
  pipe_scale_links(field="link_id",fun="count") %>%  
  make_print_map
```

```{r}
ll %>%    
  pipe_find_factors(value="sed yield") %>%
  pipe_bundle_links(field="1. Sex") %>% 
  pipe_color_links(field="1. Sex",fun="unique") %>% 
  pipe_label_links(field="link_id",fun="percent") %>%  
  pipe_scale_links(field="link_id",fun="count") %>%  
  make_print_map
```

```{r}
ll %>%    
  pipe_find_factors(value="sed yield") %>%
  pipe_bundle_links(field="1. Sex") %>% 
  pipe_color_links(field="1. Sex",fun="unique") %>% 
  pipe_label_links(field="source_id",fun="percent") %>%  
  pipe_scale_links(field="source_id",fun="percent") %>%  
  make_print_map

```

```{r}
ll %>%    
  pipe_find_factors(value="sed yield",down=0) %>%
  pipe_bundle_links(field="1. Sex") %>% 
  pipe_color_links(field="source_id",fun="percent") %>% 
  pipe_label_links(field="source_id",fun="percent") %>%  
  pipe_scale_links(field="source_id",fun="count") %>%  
  make_print_map

```

### Surprise

```{r}
ll %>%    
  pipe_find_factors(value="sed yield",down=0) %>%
  pipe_bundle_links(field="1. Sex") %>% 
  pipe_color_links(field="1. Sex",fun="unique") %>% 
  pipe_label_links(field="source_id",fun="surprise") %>%  
  pipe_scale_links(field="source_id",fun="count") %>%  
  make_print_map

```

```{r}
ll %>%    
  pipe_find_factors(value="sed yield",down=0) %>%
  pipe_bundle_links(field="1. Sex") %>% 
  pipe_label_links(field="1. Sex",fun="unique") %>% 
  pipe_color_links(field="source_id",fun="surprise") %>%  
  pipe_scale_links(field="source_id",fun="count") %>%  
  make_print_map

```


## Recalculating

```{r}
ll %>% 
  pipe_find_factors(value="WASH") %>% 
  pipe_color_factors(field="betweenness") %>% 
  make_interactive_map

ll %>% 
  pipe_find_factors(value="WASH") %>% 
  pipe_recalculate_factors() %>% 
  pipe_color_factors(field="betweenness") %>% 
  make_interactive_map

```

## Mark links

```{r}
so %>% 
  pipe_label_links(field = "source_id",fun="literal") %>% 
  pipe_mark_links(field="source_id") %>% 
  make_print_map

e3 %>% 
  pipe_label_links(field = "source_id",fun="literal") %>% 
  pipe_mark_links(field="source_id") %>% 
  make_print_map

ee %>% 
  pipe_label_links(field = "source_id",fun="literal") %>% 
  pipe_mark_links(field="source_id") %>% 
  make_print_map


so %>% 
  pipe_bundle_links(field = "source_id") %>% 
  pipe_label_links(field = "source_id",fun="literal") %>% 
  pipe_mark_links(field="source_id") %>% 
  make_print_map

so %>% 
  pipe_combine_opposites() %>% 
  pipe_bundle_links(field = "flipped_bundle") %>% 
  pipe_label_links(field = "source_id",fun="literal") %>% 
  pipe_mark_links(field="source_id") %>% 
  make_print_map

ll %>% 
  pipe_select_factors(5) %>% 
  pipe_bundle_links(field = "simple_bundle") %>% 
  pipe_mark_links(field="source_id") %>% 
  make_print_map


```

## Show continuity

```{r}
#original:

so %>% 
  pipe_label_links(field = "source_id",fun="unique") %>% 
  make_print_map

so %>% 
  pipe_label_links(field = "source_id",fun="unique") %>% 
  pipe_show_continuity(field="source_id",type="label") %>% 
  make_print_map
so %>% 
  pipe_label_links(field = "source_id",fun="unique") %>% 
  pipe_show_continuity(field="source_id") %>% 
  make_print_map


ee %>% 
  pipe_label_links(field = "source_id",fun="unique") %>% 
  pipe_show_continuity(field="source_id") %>% 
  make_print_map

e3 %>% 
  pipe_label_links(field = "source_id",fun="unique") %>% 
  pipe_show_continuity(field="source_id") %>% 
  make_print_map

e3 %>% 
  pipe_zoom_factors() %>% 
  pipe_show_continuity(field="source_id") %>% 
  pipe_label_links(field = "source_id",fun="unique") %>% 
  make_print_map

e3 %>% 
  pipe_bundle_factors("Flooding") %>% 
  pipe_show_continuity(field="source_id") %>% 
  pipe_label_links(field = "source_id",fun="unique") %>% 
  make_print_map

e3 %>% 
  pipe_bundle_factors("Flooding") %>% 
  pipe_bundle_links(field = "source_id") %>% 
  pipe_label_links(field = "source_id",fun="literal") %>% 
  pipe_show_continuity(field="source_id") %>% 
  make_print_map



so %>% 
  pipe_bundle_links() %>% 
  pipe_label_links(field = "source_id",fun="unique") %>% 
  pipe_show_continuity(field="source_id") %>% 
  make_print_map



so %>% 
  pipe_combine_opposites() %>% 
  pipe_label_links("link_id","literal") %>% 
  pipe_show_continuity(field="source_id") %>% 
  make_print_map

so %>% 
  pipe_combine_opposites() %>% 
  pipe_show_continuity() %>% 
  make_print_map

so %>% 
  pipe_combine_opposites() %>% 
  pipe_bundle_links(field = "flipped_bundle") %>% 
  pipe_show_continuity(field="source_id") %>% 
  pipe_label_links(field = "source_id",fun="unique") %>% 
  make_print_map




# Order should not matter, but you can't put bundle links later


so %>% 
  pipe_combine_opposites() %>% 
  pipe_show_continuity(field="source_id") %>% 
  pipe_bundle_links(field = "flipped_bundle") %>% 
  pipe_label_links(field = "source_id",fun="unique") %>% 
  make_print_map

```


```{r}
ll %>% 
  pipe_select_factors(5) %>% 
  pipe_bundle_links(field = "simple_bundle") %>% 
  pipe_scale_links(field = "link_id",fun="count") %>% 
  pipe_show_continuity(field="source_id") %>% 
  make_print_map


hz %>%
  pipe_show_continuity(field="source_id") %>% 
    make_print_map 

hz %>%
  pipe_zoom_factors(1) %>%
  pipe_show_continuity(field="source_id") %>% 
    make_print_map 



```

Group and label by sex and scale by count:

```{r }  
ll %>%
    pipe_select_factors(5) %>%
    pipe_bundle_links(field="1. Sex") %>%
    pipe_scale_links("link_id",fun = "count") %>%
    pipe_label_links("1. Sex",fun = "unique") %>%
    pipe_color_links("1. Sex",fun = "unique") %>%
    pipe_show_continuity(field="source_id") %>% 
    make_print_map

ll %>%
    pipe_select_factors(5) %>%
    pipe_find_links(field = "statement_id",value=90,operator="greater") %>%
    pipe_find_links(field = "statement_id",value=290,operator="less") %>%
    pipe_bundle_links(field="1. Sex") %>%
    pipe_scale_links("link_id",fun = "count") %>%
    pipe_label_links("source_id",fun = "unique") %>%
    pipe_color_links("1. Sex",fun = "unique") %>%
    pipe_show_continuity(field="source_id") %>% 
    make_print_map
```


## Nested maps

```{r }  
tt %>%
    pipe_zoom_factors(1) %>%
    pipe_select_factors(5) %>%
    make_interactive_map

```


```{r }  
tt %>%
    pipe_zoom_factors(1) %>%
    pipe_bundle_links() %>%
    pipe_label_links() %>%
    pipe_scale_links() %>%
    make_print_map

```

## Zooming out and showing source count

```{r }  
tt %>%
    pipe_zoom_factors(1) %>%
  pipe_bundle_links(field="simple_bundle") %>% 
  pipe_label_links(field="source_id",fun = "count") %>% 
  pipe_wrap_factors() %>% 
    make_print_map 

```

## Combining opposites


```{r}
hh %>% 
  make_print_map()
hh %>% 
  pipe_combine_opposites %>% 
  make_print_map()

# artificial arrowlabels
hh %>% 
    pipe_combine_opposites %>% pipe_update_mapfile(.,links=.$links %>% mutate(color="limegreen",taillabel=c("","","\u274C","\u274C","","\u274C"),headlabel=c("","","\u274C","\u274C","\u274C","\u274C")))  %>% make_print_map()

hh %>% 
    pipe_combine_opposites %>% pipe_update_mapfile(.,links=.$links %>% mutate(color="limegreen",taillabel=c("+","+","~","~","+","~"),headlabel=c("+","+","~","~","~","~")))  %>% make_print_map()

hh %>% 
    pipe_combine_opposites %>% pipe_update_mapfile(.,links=.$links %>% mutate(color="limegreen",arrowtail=c("","","nonetee","nonetee","","nonetee"),arrowhead=c("nonetee","","veenonenonetee","veenonenonetee","veenonenonetee","veenonenonetee")))  %>% make_print_map()



```



## Nested maps with opposites

Note colours in Interactive view

```{r }  
tt %>%
    pipe_zoom_factors(1) %>%
    pipe_combine_opposites() %>%
    pipe_select_links(3) %>%
    make_print_map
tt %>%
    pipe_zoom_factors(1) %>%
    pipe_combine_opposites() %>%
    pipe_select_links(3) %>%
    make_interactive_map

```


## Path tracing

```{r }  

cat("### Single\n")  

ee %>%    
  pipe_trace_paths(from = "Funds",to="area",length = 5) %>% 
  make_interactive_map

cat("### Case insensitive\n")  

ee %>%    
  pipe_trace_paths(from = "funds",to="aREa",length = 5) %>% 
  make_interactive_map

cat("### Failing; no paths at all\n")  

ee %>%    
  pipe_trace_paths(from = "xx",to="yy",length = 5) %>% 
  make_interactive_map

cat("### Failing; no paths\n")  
ee %>%    
  pipe_trace_paths(from = "Funds",to="yy",length = 5) %>% 
  make_interactive_map

ee %>%    
  pipe_trace_paths(from = "xx",to="Property",length = 5) %>% 
  make_interactive_map

cat("### Implicit multiple\n")  

ee %>%    
  pipe_trace_paths(from = "High",to="Damage",length = 5) %>% 
  make_interactive_map

cat("### Explicit multiple\n")  

ee %>%    
  pipe_trace_paths(from = "High",to="Property | Business",length = 5) %>% 
  make_interactive_map

ee %>%    
  pipe_trace_paths(from = "High",to="Property OR Business",length = 5) %>% 
  make_interactive_map

cat("Should this be possible?")

ee %>%    
  pipe_trace_paths(from = "High",to="Property OR Business",length = 5) %>% 
  make_interactive_map

tt %>%
  pipe_trace_paths(from = "Capabilities",to="[OP3]",length = 2) %>% 
  make_interactive_map

ee %>%    
  pipe_trace_paths(from = "Funds",to="area",length = 5) %>% 
  make_print_map()



```

### Robustness

```{r}  

ee %>%    
  pipe_trace_robustness(from = "High",to="Damage",length = 5) %>% 
  pipe_wrap_factors() %>% 
  make_print_map()

ee %>%    
  pipe_trace_robustness(from = "High",to="Damage",length = 5) %>% 
  get_robustness()

tt %>%
  pipe_trace_robustness(from = "Capabilities",to="[OP3]",length = 2) %>% 
  pipe_wrap_factors() %>% 
  make_print_map()

tt %>%
  pipe_trace_robustness(from = "Capabilities",to="[OP3",length = 2) %>% 
  pipe_wrap_factors() %>% 
  make_print_map()

tt %>%
  pipe_trace_robustness(from = "Capabilities",to="[OP3]",length = 2) %>% 
  get_robustness()

tt %>%
  pipe_trace_robustness(from = "Capabilities",to="[OP3",length = 2) %>% 
  get_robustness()

tt %>%
  pipe_trace_robustness(from = "Capabilities; [P13",to="[OP3]",length = 2) %>% 
  get_robustness()

```


```{r}
e3  %>%
  pipe_trace_robustness(from = "High",to="People moving",length = 5) %>% 
  make_print_map()

e3  %>%
  pipe_trace_robustness(from = "High",to="",length = 5) %>% 
  make_print_map()
```


```{r}
e3  %>%
  pipe_trace_robustness(from = "High",to="People moving",length = 5) %>% 
  get_robustness() %>% 
  kable
e3  %>%
  pipe_trace_robustness(from = "High",to="Flooding",length = 5) %>% 
  get_robustness() %>% 
  kable
e3  %>%
  pipe_trace_robustness(from = "High",to="Damage",length = 5) %>% 
  get_robustness() %>% 
  kable
e3  %>%
  pipe_trace_robustness(from = "External",to="Damage",length = 5) %>% 
  get_robustness() %>% 
  kable
e3  %>%
  pipe_trace_robustness(from = "External",to="Outcome",length = 5) %>% 
  get_robustness()%>% 
  kable


```


### Robustness by field

Just one source:

```{r}
ee  %>%
  pipe_trace_robustness(from = "Funds",to="Increased",length = 5,field = "source_id") %>% (get_robustness)

```



Check that opposites colouring is always preserved?

```{r}
hh  %>%
  pipe_trace_robustness(from = "Revision",to="happy",length = 5) %>% 
  pipe_combine_opposites %>% 
  make_print_map()

hh  %>%
  pipe_combine_opposites %>% 
  pipe_find_factors(value="exam") %>% 
  make_print_map()

hh  %>%
  pipe_combine_opposites %>% 
  pipe_zoom_factors() %>% 
  pipe_find_factors(value="exam") %>% 
  pipe_select_factors(2) %>% 
  pipe_select_links(3) %>% 
  make_print_map()


```


Colours in interactive map

```{r}
hh  %>%
  pipe_combine_opposites %>% 
  pipe_zoom_factors() %>% 
  make_interactive_map()


```


```{r }  
if(F){
graf <- tt1
graf$factors %>% filter(factor_id %notin% graf$links$from & factor_id %notin% graf$links$to)  %>% nrow

graf$links %>% filter(from %notin% graf$factors$factor_id & to %notin% graf$factors$factor_id)  %>% nrow

graf$links %>% filter(statement_id %notin% graf$statements$statement_id) %>% nrow
  }


```

## Cluster factors

```{r}
ee %>% 
  pipe_coerce_mapfile %>% 
  pipe_cluster_factors("Damage OR Flood") %>% 
  make_print_map
```

Pipe-able:

```{r}
ee %>% 
  pipe_cluster_factors("Damage OR Flood") %>% 
  pipe_cluster_factors("Rising") %>% 
  make_print_map
```



## Data manipulation, file management etc

### Accessing the data 

One column in one table

```{r }  
ll %>%
    pipe_find_factors(value="economic") %>%
    .$factors %>%
    .$label %>% 
  knitr::kable()
```

### Merging two maps 

```{r }  
if(T)merge_mapfile(ee,tt %>% pipe_select_factors(top=8)) %>% 
  pipe_color_factors(field="map_id") %>% 
  pipe_color_links(field="map_id",fun="unique") %>% 
  make_interactive_map

```

Note warning if factor labels are shared


```{r }  
if(T)load_mapfile("example2") %>%
  pipe_coerce_mapfile %>% 
  pipe_merge_mapfile("example2") %>% 
  pipe_color_factors(field="map_id") %>% 
  pipe_color_links(field="map_id",fun="unique") %>% 
  make_interactive_map

```

### Editing maps directly

There is no guarantee that the resulting map is still a standard mapfile.

```{r }  
ee$factors$label[1] <- "Label changed"
ee %>% make_interactive_map
```

### Editing maps with pipe_update_mapfile

There is no guarantee that the resulting map is still a standard mapfile.

```{r }  
ee %>% 
  pipe_update_mapfile(factors = ee$factors %>% mutate(label="one")) %>% 
  make_interactive_map
```

Coercing to a standard mapfile:

```{r }  
ee %>% 
  pipe_update_mapfile(factors = ee$factors %>% mutate(label="one")) %>% 
  pipe_coerce_mapfile() %>% 
  make_interactive_map
```

### Printing the filters

```{r}
# example2 %>% 
#   pipe_coerce_mapfile %>% 
#   pipe_find_links(field = "link_id",value=1)  %>% 
#   pipe_select_factors(20) %>%  
#   pipe_remove_isolated() %>% 
#   pipe_select_links(20) %>%  
#   pipe_zoom_factors() %>% 
#   pipe_find_statements(field = "text",value="Flo") %>% 
#   pipe_find_factors(value="Flo") %>%
#   pipe_remove_brackets("[") %>% 
#   pipe_trace_robustness(from = "Flood",to="Damage") %>% 
#   pipe_trace_paths(from = "Flood",to="Damage") %>% 
#   pipe_combine_opposites() %>% 
#   pipe_bundle_links() %>% 
#   pipe_label_links() %>% 
#   attr("meta") %>% 
#   str
# 
# example2 %>%
#   pipe_coerce_mapfile() %>%
#   pipe_bundle_links() %>%
#   pipe_scale_links() %>%
#   pipe_label_links() %>%
#   pipe_color_links() %>%
#   pipe_scale_factors(field = "frequency") %>%
#   pipe_label_factors() %>%
#   pipe_color_factors() %>%
#   pipe_color_borders() %>%
#   pipe_mark_links() %>%
#   pipe_show_continuity() %>%
#   pipe_cluster_factors() %>%
#   pipe_wrap_factors() %>%
#   pipe_wrap_links() %>%
#   print_filter()


```




You can also load up an Excel file:

```{r }
# system.file("extdata", "quip-lorem", package = "CausalMapFunctions") %>% 
#   get_mapfile_from_excel()

```
